\begin{appendices}
\section*{Bijlage A -- Volledige lijst van testqueries}
\addcontentsline{toc}{section}{Bijlage A -- Volledige lijst van testqueries}
\label{app:testqueries}

Onderstaande lijst bevat alle 88 testqueries die gebruikt werden voor de evaluatie van het prototype, gegroepeerd per agent en subcategorie.

\subsection*{GraphAgent (22 queries)}

\textbf{Identity}
\begin{itemize}[noitemsep]
  \item Who am I in Microsoft 365?
\end{itemize}

\textbf{E-mail}
\begin{itemize}[noitemsep]
  \item Show me my 5 most recent emails.
  \item Search for emails that have the word `meeting' in the subject.
  \item Have I received any emails in the last 7 days? List sender and subject.
  \item What does my most recent email say? Give me the full body.
  \item Show me emails I received in the last 14 days.
  \item Find emails with `invoice' in the subject.
  \item Find the most recent email with `meeting' in the subject and read its full body.
\end{itemize}

\textbf{People}
\begin{itemize}[noitemsep]
  \item Find the email address of Dorian.
  \item Look up the email address of Marie in the organization.
\end{itemize}

\textbf{Kalender}
\begin{itemize}[noitemsep]
  \item What are my upcoming calendar events this week?
  \item Search my calendar for any events or meetings in the next 14 days.
  \item How many calendar events do I have scheduled this week? List them all.
  \item Search my calendar for events scheduled in the next 30 days.
\end{itemize}

\textbf{Contacten}
\begin{itemize}[noitemsep]
  \item Show me my Microsoft 365 contacts.
  \item List my Microsoft 365 contacts and include their phone numbers.
\end{itemize}

\textbf{Bestanden}
\begin{itemize}[noitemsep]
  \item Find any Excel or PDF files in my OneDrive.
  \item Search OneDrive for a file called `report' and read its content.
  \item Find all Word documents in my OneDrive.
  \item Find a document called `agenda' in OneDrive and show its content.
  \item Search OneDrive for Excel files and read the content of the first two found.
  \item Find any files related to `budget' in OneDrive and read all of them.
\end{itemize}

\subsection*{SalesforceAgent (22 queries)}

\textbf{Accounts}
\begin{itemize}[noitemsep]
  \item List 5 Salesforce accounts.
  \item Find Salesforce accounts in Belgium, including their billing address.
  \item Find Salesforce accounts that have `Group' in their name.
  \item Show me Salesforce accounts with their phone numbers.
  \item Find Salesforce accounts in France and list the contacts linked to those accounts.
\end{itemize}

\textbf{Contacts}
\begin{itemize}[noitemsep]
  \item Show me 5 Salesforce contacts with their email addresses.
  \item Find Salesforce contacts in the Sales department.
  \item Find Salesforce contacts with `Manager' in their title.
  \item Show me the most recently created Salesforce contacts.
\end{itemize}

\textbf{Leads}
\begin{itemize}[noitemsep]
  \item Show me 5 leads in Salesforce.
  \item Find Salesforce leads from the Technology or Software industry.
  \item Find Salesforce leads that have been converted.
  \item Show me Salesforce leads with the status `Open - Not Contacted'.
\end{itemize}

\textbf{Opportunities}
\begin{itemize}[noitemsep]
  \item List 5 open opportunities in Salesforce.
  \item Show me Salesforce opportunities with an amount greater than 10,000. Include probability.
  \item Show me Salesforce opportunities in the `Proposal/Price Quote' stage.
  \item List Salesforce opportunities sorted by amount, highest first.
  \item Show me the 3 largest open Salesforce opportunities and the billing country of each related account.
\end{itemize}

\textbf{Cases}
\begin{itemize}[noitemsep]
  \item List open support cases in Salesforce.
  \item Show me 5 closed Salesforce cases including their close date and description.
  \item Find high-priority open cases in Salesforce.
  \item Show me Salesforce cases with their related account names.
\end{itemize}

\subsection*{SmartSalesAgent (22 queries)}

\textbf{Locaties}
\begin{itemize}[noitemsep]
  \item List all SmartSales locations.
  \item Find SmartSales locations in Brussels.
  \item List SmartSales locations in Belgium sorted by name, using full projection.
  \item List all SmartSales locations, then retrieve the full details of the first result.
  \item What fields are available to display in the SmartSales location list?
  \item What fields can I use to filter SmartSales locations?
  \item What fields can I use to sort SmartSales locations?
\end{itemize}

\textbf{Catalogus}
\begin{itemize}[noitemsep]
  \item List SmartSales catalog items.
  \item List SmartSales catalog items with simple projection, sorted by name.
  \item List SmartSales catalog items, then retrieve the full details of the first one.
  \item What fields can be displayed for SmartSales catalog items?
  \item What fields can I filter SmartSales catalog items by?
  \item What fields can I sort SmartSales catalog items by?
\end{itemize}

\textbf{Orders}
\begin{itemize}[noitemsep]
  \item List recent SmartSales orders.
  \item List SmartSales orders with full projection.
  \item List SmartSales orders, then retrieve the full details of the first order.
  \item What is the SmartSales order configuration?
  \item List all SmartSales order approbation statuses.
  \item List SmartSales approbation statuses, then get the full details of the first one.
  \item What fields can be displayed for SmartSales orders?
  \item What fields can I filter SmartSales orders by?
  \item What fields can I sort SmartSales orders by?
\end{itemize}

\subsection*{OrchestratorAgent (22 queries)}

\textbf{Routing queries}
\begin{itemize}[noitemsep]
  \item Who am I in Microsoft 365?
  \item List 5 Salesforce accounts.
  \item List SmartSales locations.
  \item What calendar events do I have next week?
  \item Search my emails for anything about budget.
  \item Find all open Salesforce opportunities with an amount above 10,000.
  \item List SmartSales catalog items.
  \item Show me recent SmartSales orders.
\end{itemize}

\textbf{Cross-system queries}
\begin{itemize}[noitemsep]
  \item Find contacts named `John' in both Microsoft 365 and Salesforce.
  \item Show me my calendar events for the next 7 days and check whether any organizers appear as contacts in Salesforce.
  \item List SmartSales locations in Brussels and check if there are any matching Salesforce accounts in the same city.
  \item What are my 3 most recent emails? Are any of those senders listed as contacts in Salesforce?
  \item Show me open Salesforce opportunities and SmartSales locations in Belgium. Give me a summary of both.
  \item Find my 5 most recent emails and check if any of the senders are Salesforce leads.
  \item List my Microsoft 365 contacts and check if any of them are also SmartSales locations.
  \item Find Salesforce accounts in Brussels and compare with SmartSales locations in the same city.
  \item Show me my calendar events for the next 7 days and check if any attendees are Salesforce contacts.
  \item Who am I in Microsoft 365, what Salesforce accounts exist, and what SmartSales locations are in Belgium?
  \item List recent SmartSales orders and check if the customer names match any Salesforce accounts.
  \item Search my OneDrive for files about contracts and check if the mentioned company names are Salesforce accounts.
  \item Find emails I received this week and check if any senders are linked to a SmartSales location.
  \item Give me an overview of my upcoming meetings from Microsoft 365, related Salesforce opportunities, and SmartSales locations for the companies involved.
\end{itemize}

\end{appendices}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    Dutch version           %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{appendices}
% \section*{Bijlage A}
% \addcontentsline{toc}{section}{Bijlage A}  

% Toelichting bijlage.



% \newpage
% \section*{Bijlage B}
% \addcontentsline{toc}{section}{Bijlage B}  

% Toelichting bijlage.

% \end{appendices}
